\section{Two-Digit Postcodes}
CSV Data provided by geonames.org \cite{Unxos2019} and postcode.info, which was scrapped and provided by a fellow student \cite{Mehra2019},  was used as basis for calculating two-digit postcodes for European countries. At the first iteration two-digit postcodes were calculated from Geonames data. In order to achieve this Python scripts were written \cite{Dechant2019b}. These scripts process a Geonames CSV file and provide a new CSV file with two-digits postcodes including their centroids. Here is an example of six calculated two-digit postcodes in Germany:

\begin{table}[H]
\centering
\begin{tabular}{|l|l|l|l|l|l|}
\hline
DE80 & geonames2d & 80 & postalcode & 48.1615 & 11.5509 \\ \hline
DE81 & geonames2d & 81 & postalcode & 48.1254 & 11.5726 \\ \hline
DE82 & geonames2d & 82 & postalcode & 47.911  & 11.2502 \\ \hline
DE83 & geonames2d & 83 & postalcode & 47.8713 & 12.2803 \\ \hline
DE84 & geonames2d & 84 & postalcode & 48.4086 & 12.4327 \\ \hline
DE85 & geonames2d & 85 & postalcode & 48.4174 & 11.6308 \\ \hline
\end{tabular}
\caption{Geonames Two-Digit Postcodes}
\label{tab:geonames2d}
\end{table}

At the second iteration Geonames and Postcode data were combined after having done some preparation steps on the Postcode data. Again Python scripts were written \cite{Dechant2019}. Here is an excerpt:

\begin{table}[H]
\centering
\begin{tabular}{|l|l|l|l|l|l|}
\hline
DE80 & geonamesandpostcodeinfo & 80 & postalcode & 48.1512 & 11.5938 \\ \hline
DE81 & geonamesandpostcodeinfo & 81 & postalcode & 48.1331 & 11.6046 \\ \hline
DE82 & geonamesandpostcodeinfo & 82 & postalcode & 47.9419 & 11.2759 \\ \hline
DE83 & geonamesandpostcodeinfo & 83 & postalcode & 47.888 & 12.2627 \\ \hline
DE84 & geonamesandpostcodeinfo & 84 & postalcode & 48.4367 & 12.4206 \\ \hline
DE85 & geonamesandpostcodeinfo & 85 & postalcode & 48.4171 & 11.6294 \\ \hline
\end{tabular}
\caption{Geonames and Postcode.info Two-Digit Postcodes}
\label{tab:geonamesandpostcodeinfo2d}
\end{table}

Comparing these two tables one can see that the coordinates changed slightly. This is due to the fact that now two different data sources were used for the calculation of centroids resulting in more accurate coordinates.
Postcodes in Malta were aggregated and their centroids calculated using the first three digits as requested by one of the project's experts.
Finally the calculated two-digit postcodes had to be imported into Pelias. For this a Python script, which creates a CSV file conforming to Pelias' custom data importer, had to be written \cite{Dechant2019}. This CSV file has to be copied to the following path, which is defined in docker-compose.yml and .env:
/data/pelias-docker-compose/geonamesandpostcodeinfo/geonamesandpostcodeinfo2Dpostalcodes.csv
Afterwards the command "pelias import csv" has to be run. Once the import is complete, the custom layer "geonamesandpostcodeinfo" and its data can be queried as follows:\\

\url{http://141.59.29.110:4000/v1/search?text=DE81&sources=geonamesandpostcodeinfo}\\

This query delivers the following JSON file:\\
\begin{lstlisting}[language=json,breaklines=true]
"type": "FeatureCollection",
    "features": [
 		{
	"type": "Feature",
	"geometry": {
	   "type": "Point",
	   "coordinates": [
	   	11.6046,
		48.1331 
	]
	},
"properties": {
	"id": "1141",
	"gid": "geonamesandpostcodeinfo:postalcode:1141",
	"layer": "postalcode",
	"source": "geonamesandpostcodeinfo",
	"source_id": "1141",
	"name": "DE81",
	"confidence": 1,
	"match_type": "exact",
	"distance": 690.624,
	"accuracy": "centroid",
	"country": "Germany",
	"country_gid": "whosonfirst:country:85633111",
	"country_a": "DEU",
	"region": "Bayern",
	"region_gid": "whosonfirst:region:85682571",
	"region_a": "BY",
	"macrocounty": "Oberbayern",
	"macrocounty_gid": "whosonfirst:macrocounty:404227567",
	"county": "Muenchen",
	"county_gid": "whosonfirst:county:102063261",
	"county_a": "MN",
	"locality": "Muenchen",
	"locality_gid": "whosonfirst:locality:101748479",
	"neighbourhood": "Haidhausen",
	"neighbourhood_gid": "whosonfirst:neighbourhood:85905613",
	"continent": "Europe",
	"continent_gid": "whosonfirst:continent:102191581",
	"label": "DE81, Muenchen, Germany"
		}
	}
],
"bbox": [
	11.6046,
	48.1331,
	11.6046,
	48.1331
	]
}
\end{lstlisting}

